### 2016-09-06 Documents/bootcamp_topic_pandas-clean.tex
rebuild all text documents to show updated header and date (#10)

\bigskip\bigskip
\centerline{\Large \bf Topic Outline:  Cleaning \& Shaping Data}
\centerline{Revised: \today}

@@

\item {\bf Want operator}
\begin{itemize}
\item Keep in mind what we want, then figure out how to get there
\item Problems:  numbers contain dollar signs or commas, interpreted as strings;
missing values not marked;
dataset contains a lot of stuff we don't want; rows and columns are flipped.
\end{itemize}

@@

\item Boolean selection
\begin{itemize}
\item Things we use
\item Comparisons, boolean selection, the {\tt isin} method
\end{itemize}

@@

\section*{Pandas 3:  Data shaping}

%{\small
\url{https://github.com/NYUDataBootcamp/Materials/blob/master/Code/IPython/bootcamp_pandas-shape.ipynb}
%}

In short:  GitHub $\Rightarrow$ Code $\Rightarrow$ IPython $\Rightarrow$
 \verb|bootcamp_pandas-shape.ipynb| $\Rightarrow$ Raw

\item Want operator
\begin{itemize}
\item Problem:  Rows and columns are switched, or worse
\end{itemize}

\item Setting and resetting the index
\item Multi-indexes
\item Switching rows and columns, pivoting
\item Stacking and unstacking:  the components of pivoting
\end{itemize}

>>>>

\bigskip\bigskip
\centerline{\Large \bf Topic Outline:  Cleaning Data}
\centerline{Revised: \today}

@@

\item {\bf Want operator}
\begin{itemize}
\item Keep in mind what we want, then figure out how to get there
\item Examples:  numbers contain dollar signs or commas, interpreted as strings;
missing values not marked;
dataset contains a lot of stuff we don't want; rows and columns are flipped.
\end{itemize}

@@

\item Boolean selection
\begin{itemize}
\item Things we use --- a lot
\item Comparisons, boolean selection
\item The {\tt isin} and {\tt contains} methods
\end{itemize}

@@
